\documentclass[11pt, a4paper, twocolumn]{article}

\usepackage{style}

% Information for generating title
\title{\bfseries Machine Learning: Project 1}
\author{\textbf{Olivier Stähli} \\ \href{mailto:olivier.staehli@epfl.ch}{olivier.staehli@epfl.ch}
   \and \textbf{Ivan Bioli} \\ \href{mailto:ivan.bioli@epfl.ch}{ivan.bioli@epfl.ch}
   \and \textbf{Fabio Matti} \\ \href{mailto:fabio.matti@epfl.ch}{fabio.matti@epfl.ch}}
\date{}

\begin{document}

% Escaping twocolumn-layout to generate titlelines and abstract
\twocolumn[
  \begin{@twocolumnfalse}
    \vspace{-1.5cm}
    \maketitle
    \begin{abstract}
        Text for the abstract.
    \end{abstract}
    \vspace{0.75cm}
  \end{@twocolumnfalse}
]

\section{Introduction}
\label{sec:introduction}

What is the underlying problem, and what are we allowed/supposed to do (i.e.
rules, guidelines, the 6 regressors, linear models).

\section{Models and Methods}
\label{sec:models}

Summarize the data set (30 numerical features, binary label slightly skewed,
250000 training samples and 750000 test samples?, outliers were replaced with
-999).

\subsection{Preprocessing}
\label{subsec:preprocessing}

Describe our approach to preprocessing (feature importances, outliers,
standardization, polynomial basis).

[Visualizations of feature preprocessing/importance]

\subsection{Implementations}
\label{subsec:implementations}

Detail our way of implementing the regressors (robustness, converting 1D to 2D
numpy arrays such that any numpy array can be passed, documentation with usage,
encapsuled code within each function, stopping criterion where it makes sense).

Hyperparameter tuning (crossvalidation, grid search for ideal parameters).

[Maybe visualization of parameter grid search]

Optimized regressor.

\section{Results}
\label{sec:results}

Submitted predictions to AIcrowd.

\begin{table}[h]
    \caption{Results of the regressors}
    \label{tab:results}
    \centering
    \renewcommand{\arraystretch}{1.2}
    \begin{tabular}{@{}lcc@{}}
        \toprule
        Regressor & F1-score & Accuracy \\
        \midrule
        least\_squares\_GD & 0.665 & 0.712 \\
        least\_squares\_SGD & 0.665 & 0.712 \\
        least\_squares & 0.665 & 0.712 \\
        ridge\_regression & 0.665 & 0.712 \\
        logistic\_regression & 0.665 & 0.712 \\
        reg\_logistic\_regression & 0.665 & 0.712 \\
        optimized\_regressor & 0.665 & 0.712 \\
        \bottomrule
    \end{tabular}
\end{table}

\section{Discussion}
\label{sec:discussion}

Problems we encountered.

Shortcomings of our regressors.

\section{Summary}
\label{sec:summary}

(May not be necessary for such a short report).

\bibliography{biblio.bib}

\end{document}